%-------------------------
% Resume in Latex
% Author : Biswas Simkhada
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Biswas Simkhada} \\ \vspace{1pt}
    \small +61 433 760 421 $|$ \href{mailto:biswas.simk@gmail.com}{\underline{biswas.simk@gmail.com}} $|$ 
    \href{https://linkedin.com/in/biswas-simkhada}{\underline{linkedin.com/in/biswas-simkhada}} $|$
    \href{https://github.com/biswas57}{\underline{github.com/biswas57}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of New South Wales}{Expected Graduation: Dec 2025}
      {\emph{Bachelor of Computer Science}}{\emph{Kensington, NSW}}
      \resumeItem{Relevant Coursework: Data Structures and Algorithms, Object Oriented Programming, Database Systems, Computer System Architecture, Team Software Development, Shell Scripting, Frontend Engineering, Cybersecurity Engineering.}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sales Team Leader}{Feb 2023 -- Oct 2023}
      {\emph{Be Interactive Australia}}{\emph{Haymarket, NSW}}
      \resumeItemListStart
        \resumeItem{Thrived in a direct sales environment, generating \$700 a day, totalling over \$75,000 in sales within 9 months.}
        \resumeItem{Recruited, trained, and led a team of 8 sales representatives, enhancing their sales strategies in a team setting.}
        \resumeItem{Educated the team on utilizing Law of Averages and Impulse Factors in pitches to improve performance and enable representatives to leverage customer decision-making moments, leading to a 25\% increase in team sales.}
        \resumeItem{Consistently surpassed monthly team sales targets by 16\%, exceeding the business' weekly sales goal of \$60,000.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%       
%   \resumeSubheading
%      {Information Technology Support Specialist}{Sep. 2018 -- Present}
%      {Southwestern University}{Georgetown, TX}
%      \resumeItemListStart
%        \resumeItem{Communicate with managers to set up campus computers used on campus}
%        \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
%        \resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
%    \resumeItemListEnd
%
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Software Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Tributary Event Processing System} $|$ Java, JUnit, Mockito, JSON, Gradle}{Mar 2024 -- Apr 2024}
          \resumeItemListStart
            \resumeItem{Constructed a Multi-Type Event Processing System API in Java, with parallel data processing and assured type-safety by implementing Concurrency and Generics alongside important OOP Design principles.}
            \resumeItem{Incorporated key OOP Design patterns such as Singleton \& Abstract Factory patterns to compact and synchronize event production consumption, and Strategy \& Observer patterns to streamline event allocation.}
            \resumeItem{Achieved \(\sim \)85\% testing coverage by conducting over 75 tests in JUnit and Mockito to ensure system reliability.}
            \resumeItem{Designed a message replay feature to allow events to be replayed from specific offsets, enabling error checking and correction without compromising system performance.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Kahoot! Emulator} $|$ TypeScript, JavaScript, Node.js, Express, JSON, npm, Vercel}{Sep 2023 -- Nov 2023}
          \resumeItemListStart
            \resumeItem{Engineered a Kahoot! emulator API named 'Toohak!' utilizing TypeScript and JavaScript alongside the Node.js and Express frameworks, and learning deployment fundamentals through Vercel for scalability and performance.}
            \resumeItem{Collaborated in a team of 5 using Gitlab to program the RESTful API with a full suite of HTTP requests, while reaching key project milestones over the course of 2 months.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%-----------EXTRACURRICULAR-----------
\section{Extracurricular Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Accenture Software Engineering Program} $|$ {Forage}}{Apr 2024 -- May 2024}
          \resumeItemListStart
            \resumeItem{Integrated a search functionality into an e-commerce platform's RESTful API with Java and Spring Boot, followed by conducting over 50 unit tests in Spock to guarantee features performed correctly.}
            \resumeItem{Participated in an Agile session, discussing and breaking down software features into sets of smaller user stories.}
            \resumeItem{Focused on key user deliverables such as shipping options, payment processing, and shopping cart features.}
            \resumeItem{Designed and established a CI/CD testing pipeline with Gradle and Jenkins to create automated tests across all GitHub repository branches, resulting in greatly enhanced efficiency when testing and merging code.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Atlassian x UNIHACK Hackathon 2024} $|$ {UNIHACK}}{Feb 2024 -- Mar 2024}
          \resumeItemListStart
            \resumeItem{Programmed a website called Bis' Kitchen with a team of 4 to display a range of cultural dishes and recipes.}
            \resumeItem{Contended for UNIHACK's Most Engaging Pitch Award with a compelling video walkthrough of Bis’ Kitchen.}
            \resumeItem{Developed an interactive front-end for Bis' Kitchen in React and HTML, while integrating an external API, React Routers and other styling components to build a complete and functional UI.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Computer E-commerce Store} $|$ {eBay.com}}{Aug 2019 -- Sep 2022}
          \resumeItemListStart
            \resumeItem{Operated an eBay store specialising in refurbished desktops, generating over \$20,000 in revenue over 3 years.}
            \resumeItem{Sold over 2,000 units consisting of RAM, CPU, GPU, and Desktops with a customer approval rate of 99.5\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:}{ Java, Python, SQL, JavaScript, C, HTML, CSS.} \\
     \textbf{Frameworks:}{ JUnit, React.js, Node.js, Express, TypeScript.} \\
     \textbf{Developer Tools:}{ Git, GitLab, GitHub, PostgreSQL, Gradle, npm, Homebrew, Vercel, Visual Studio Code.} \\
     \textbf{Hobbies and Interests:}{ History \& Religion, Boxing, Poetry.}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
